% Copyright 2020-2023 Robert Bosch GmbH

% Licensed under the Apache License, Version 2.0 (the "License");
% you may not use this file except in compliance with the License.
% You may obtain a copy of the License at

% http://www.apache.org/licenses/LICENSE-2.0

% Unless required by applicable law or agreed to in writing, software
% distributed under the License is distributed on an "AS IS" BASIS,
% WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
% See the License for the specific language governing permissions and
% limitations under the License.

\begin{packagehistory}

    \historyversiondate{0.0.1}{11/2024}
    \historychange{Initial version}

    \historyversiondate{0.1.0}{01/2025}
    \historychange{- Add component mapping as prefix destination title in configuration json file.\newline
- Let not assign issue as unassigned (on RTC) instead of logged in user.\newline
- Add new feature (optional argument  --nosync) to process issue 'nosync' label.}

    \historyversiondate{0.2.0}{01/2025}
    \historychange{- Add configurations to support user-defined workflow (state transitions) in RTC.\newline
- Add a new feature (optional argument --status-only) to update only the status of synced issues.}

    \historyversiondate{0.2.1}{02/2025}
    \historychange{- Add priority information for syncing.\newline
- Update behavior when syncing assginee and sprint information.}

    \historyversiondate{0.2.2}{02/2025}
    \historychange{- Improve the console message when syncing fails.\newline
- Add sprint version mapping for labeling original ticket with product's version.\newline
- Update the behavior to continue with the next issue instead of terminating when an error occurs during syncing or issue creation.}

    \historyversiondate{0.2.3}{03/2025}
    \historychange{Fix issue when adding label to closed ticket on JIRA}

    \historyversiondate{0.2.4}{03/2025}
    \historychange{Use labels \plog{in work} and \plog{ready for verifying} for \pcode{In Progress} and \pcode{Done} status}

    \historyversiondate{0.3.0}{03/2025}
    \historychange{Introduce new feature to sync Epic and its relationship}

    \historyversiondate{0.3.1}{03/2025}
    \historychange{Update the behavior of \pcode{priority}:\newline
    - If the priority is not set in destination issue, sync it from original issue to destination.\newline
    - Otherwise, sync priority back from destination to original issue.
    }

    \historyversiondate{0.3.2}{03/2025}
    \historychange{- Update the behavior of \pcode{story point} and \pcode{assignee} to sync back the value from the destination if it is set.\newline
- Add new configuration \pcode{project_scope} for RTC tracker to set project scope when creating new work item.
    }

    \historyversiondate{0.3.3}{05/2025}
    \historychange{- Add new configuration \pcode{planned_for} for RTC tracker to set default \pcode{Planned For} when creating new work item.\newline
- Add feature to sync (update or create) \pcode{Sprint} of issue back to Jira with configured board ID.
    }

    \historyversiondate{0.3.4}{05/2025}
    \historychange{Update tool to fetch latest data of each issue before syncing.}

    \historyversiondate{0.3.5}{06/2025}
    \historychange{Update tool to support status labels - with underscore of Jira ticket.}
\end{packagehistory}
